---
title: "explore_return"
author: "Michael She"
date: "10/25/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(forcats)
library(tidyverse)
library(lubridate)
library(data.table)
library(ggplot2)
library(ggalluvial)
library(stargazer)

ggplot2::theme_set(ggplot2::theme_bw())
```

```{r}
df_campaign <- fread('../data/engineered_factset_campaign.csv')
df_pricing <- fread('../data/clean_factset_pricing.csv') %>% .[, date := as.Date(date)]
df_index <- fread('../data/yahoo_finance_pricing.csv')
df_tweets <- fread('../data/twitter_tweets.csv')

df_campaign_mapping <- fread('../mapping/campaign_mapping.csv')

df_campaign <- merge(df_campaign, df_campaign_mapping, by = "campaign_objective_primary", all.x = TRUE, all.y = FALSE)
```


```{r}
df_plot <- df_pricing %>%
  .[company_id == "0GGD8K-E"] %>%
  .[, volatility := sd(stock_daily_return, na.rm = TRUE)] %>%
  .[, announcement_price := price[date == "2018-04-16"]] %>%
  .[, announcement_time := difftime(date, as.Date("2018-04-15"), units = "days") %>% as.numeric] %>% 
  .[date %between% c("2018-04-15", "2019-04-15"), price_upper := announcement_price + sqrt(announcement_time) * announcement_price * volatility * 2] %>%
  .[date %between% c("2018-04-15", "2019-04-15"), price_lower := announcement_price - sqrt(announcement_time) * announcement_price * volatility * 2] %>%
  .[date %between% c("2018-04-15", "2019-04-15"), price_predicted := announcement_price + announcement_price * announcement_time * 0.025 / 30] %>%
  .[date %between% c("2016-10-15", "2019-04-15")] 

df_plot %>%
  ggplot() +
  geom_line(aes(x = date, y = price, color = "actual")) + 
  geom_line(aes(x = date, y = price_predicted, color = "predicted")) + 
  geom_line(aes(x = date, y = price_upper)) +
  geom_line(aes(x = date, y = price_lower)) +
  geom_ribbon(aes(x = date, ymin = price_lower, ymax = price_upper), fill = "lightblue", alpha = 0.3) +
  geom_vline(xintercept = as.Date("2018-10-15"), linetype = 2) +
  scale_y_continuous(labels = scales::dollar) +
  labs(
    title = "Predicted and Actual Campaign Returns for Dell Technologies, Inc. / Carl C. Icahn",
    subtitle = "Campaign announced on 2018-10-15 to seek higher price for merger",
    color = "Predicted vs. Actual",
    x = "Date", y = "Price"
  )
```

```{r}
df_campaign %>%
  .[cumulative_6m_residual_return <= 1] %>%
  ggplot() + 
  geom_histogram(aes(x = cumulative_6m_residual_return)) +
  geom_vline(aes(xintercept = median(df_campaign$cumulative_6m_residual_return, na.rm = TRUE), color = "median"), size = 1) +
  geom_vline(aes(xintercept = mean(df_campaign$cumulative_6m_residual_return, na.rm = TRUE), color = "mean"), size = 1) +
  scale_x_continuous(labels = scales::percent) +
  labs(
    title = "Histogram of Cumulative Abnormal Monthly Returns for Activist Campaigns",
    subtitle = "Market-adjusted returns from -6 months to +6 months around announcement (9,571 Campaigns from 1984 to 2018)",
    y = "Frequency",
    x = "Campaign Return",
    color = "Statistic"
  )
```

```{r}
df_campaign %>%
  .[!is.na(cumulative_6m_residual_return)] %>%
  .[, cumulative_6m_residual_return_is_positive := ifelse(cumulative_6m_residual_return > 0, "Positive Camapign Return", "Negative Campaign Return")] %>%
  .[, .N, by = list(campaign_objective_code, cumulative_6m_residual_return_is_positive)] %>%
  .[N >= 150] %>%
  .[order(N, decreasing = TRUE)] %>%
  .[, campaign_objective_code := forcats::as_factor(campaign_objective_code)] %>%
  ggplot(aes(axis1 = campaign_objective_code, axis2 = cumulative_6m_residual_return_is_positive, y = N)) +
  geom_alluvium(aes(fill = cumulative_6m_residual_return_is_positive)) +
  geom_stratum() +
  geom_text(stat = "stratum", label.strata = TRUE) +
  scale_x_discrete(limits = c("Campaign Objective", "Campaign Return"), expand = c(.1, .05)) +
  theme_minimal() +
  labs(
    title = "Campaign Objectives and Campaign Returns",
    subtitle = "Counts of campaigns objectives and their particular return outcomes (9,571 Campaigns from 1984 to 2018)",
    y = "Count of Campaigns",
    fill = "Campaign Return Direction"
  ) +
  theme(legend.position = 'bottom')
```


# Data

```{r}
nan_mean <- purrr::partial(mean, na.rm = TRUE)
nan_median <- purrr::partial(median, na.rm = TRUE)

df_campaign_mapping <- fread('mapping/campaign_mapping.csv')
df_value_mapping <- fread('mapping/value_demand_mapping.csv')
df_proxy_mapping <- fread('mapping/proxy_result_mapping.csv')

df <- fread(
  'data/engineered_factset_campaign_data.csv',
  stringsAsFactors = TRUE,
  na.strings = c("", "NA", "#N/A")
) %>%
  .[, campaign_announcement_date := as.Date(campaign_announcement_date)] %>%
  .[campaign_announcement_date >= as.Date("1995-01-01")]

df <- df %>%
  .[, campaign_objective_primary := forcats::fct_explicit_na(campaign_objective_primary)] %>%
  merge(df_campaign_mapping, by = "campaign_objective_primary", all.x = TRUE, all.y = FALSE) %>%
  .[, campaign_objective_group :=  forcats::as_factor(campaign_objective_group)]

df <- df %>%
  .[, value_demand := forcats::fct_explicit_na(value_demand)] %>%
  merge(df_value_mapping, by = "value_demand", all.x = TRUE, all.y = FALSE) %>%
  .[, value_demand_group :=  forcats::as_factor(value_demand_group)]

df <- df %>%
  .[, governance_demand := forcats::fct_explicit_na(governance_demand)]

df <- df %>%
  .[, proxy_campaign_winner_or_result := forcats::fct_explicit_na(proxy_campaign_winner_or_result)] %>%
  merge(df_proxy_mapping, by = "proxy_campaign_winner_or_result", all.x = TRUE, all.y = FALSE) %>%
  .[, proxy_campaign_result_group := forcats::as_factor(proxy_campaign_result_group)]

df <- df %>%
  .[, number_of_board_seats_gained := fifelse(is.na(number_of_board_seats_gained), 0, number_of_board_seats_gained)] %>%
  .[, board_seats_percentage_gained := number_of_board_seats_gained / number_of_board_seats_sought] %>%
  .[, board_seats_result := dplyr::case_when(
    board_seats_percentage_gained >= 1 ~ 'Dissident',
    board_seats_percentage_gained > 0 ~ 'Management',
    board_seats_percentage_gained <= 0 ~ 'Fail'
  )] %>%
  .[, board_seats_result := forcats::as_factor(board_seats_result)] %>%
  .[, board_seats_result := forcats::fct_explicit_na(board_seats_result)] 
  
df <- df %>%
  .[, return_result := fifelse(cumulative_6m_residual_return > 0, "positive_return", "negative_return")] %>%
  .[, return_result := fifelse(is.na(return_result), "unknown_return", return_result)] %>%
  .[, return_result := forcats::as_factor(return_result)]

```

## Summaries

```{r}
glimpse(df)
```

```{r}
df[, .N, keyby = lubridate::ceiling_date(campaign_announcement_date, unit = "1 year")] %>% print
```


```{r}
df[, .N, by = campaign_objective_primary] %>% setorder(N) %>% print
```

```{r}
df[, .N, by = value_demand] %>% setorder(N) %>% print
```

```{r}
df[, .N, by = governance_demand] %>% setorder(N) %>% print
```

```{r}
df[, .N, by = proxy_campaign_winner_or_result] %>% setorder(N) %>% print
```

```{r}
df[, .N, by = proxy_campaign_result_group] %>% setorder(N) %>% print
```

```{r}
df[, .N, by = board_seats_result] %>% setorder(N) %>% print
```

```{r}
df[, .N, by = return_result] %>% setorder(N) %>% print
```

```{r}
df[value_demand_group == "Unused", list(value_demand_group, value_demand)]
```


# Visualizations

```{r}
df_total_returns <- df %>%
  melt.data.table(
    id.vars = c(
      "campaign_id",
      "campaign_announcement_date",
      "campaign_objective_primary",
      "glass_lewis_support",
      "iss_support",
      "ownership_pecent_on_announcements"
    ),
    measure.vars = c(
      "pre_18m_total_return",
      "pre_12m_total_return",
      "pre_6m_total_return",
      "post_6m_total_return",
      "post_12m_total_return", 
      "post_18m_total_return"
    ),
    variable.name = c("return_period"),
    value.name = c("return_value")
  )

df_residual_returns <- df %>%
  melt.data.table(
    id.vars = c(
      "campaign_id",
      "campaign_announcement_date",
      "campaign_objective_primary",
      "glass_lewis_support",
      "iss_support",
      "ownership_pecent_on_announcements"
    ),
    measure.vars = c(
      "pre_18m_residual_return",
      "pre_12m_residual_return",
      "pre_6m_residual_return",
      "post_6m_residual_return",
      "post_12m_residual_return", 
      "post_18m_residual_return"
    ),
    variable.name = c("return_period"),
    value.name = c("return_value")
  )

df_returns <- list(total = df_total_returns, residual = df_residual_returns) %>%
  rbindlist(use.names = TRUE, fill = TRUE, idcol = "return_type")

df_average_returns <- df_returns %>%
  .[
    j = list(return_value = mean(return_value, na.rm = TRUE)),
    keyby = list(return_type, return_period)
  ]

df_yearly_returns <- df_returns %>%
  .[
    j = list(return_value = mean(return_value, na.rm = TRUE)),
    keyby = list(return_type, return_period, campaign_announcement_date = lubridate::ceiling_date(campaign_announcement_date, unit = "1 year"))
  ]
```

```{r}
df_yearly_returns %>%
  .[return_period %in% c("post_12m_total_return", "post_12m_residual_return")] %>%
  ggplot() +
  geom_col(aes(x = campaign_announcement_date, y = return_value, fill = return_period), position = "dodge") +
  facet_wrap(~return_type, ncol = 1)
```

```{r}
df_returns %>%
  ggplot() +
  geom_boxplot(aes(x = glass_lewis_support, y = return_value, fill = return_period), outlier.shape = NA, position = "dodge") +
  geom_hline(yintercept = 0) +
  facet_wrap(~return_type, ncol = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(-0.15, 0.15)
```

```{r}
df_returns %>%
  ggplot() +
  geom_boxplot(aes(x = iss_support, y = return_value, fill = return_period), outlier.shape = NA, position = "dodge") +
  geom_hline(yintercept = 0) +
  facet_wrap(~return_type, ncol = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(-0.15, 0.15)
```


```{r}
df_returns %>%
  ggplot() +
  geom_boxplot(aes(x = campaign_objective_primary, y = return_value, fill = return_period), outlier.shape = NA, position = "dodge") +
  facet_wrap(~return_type, ncol = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(-0.15, 0.15)
```

## Return Bars

```{r}
df %>%
  ggplot() +
  geom_boxplot(aes(x = reorder(proxy_campaign_winner_or_result, cumulative_6m_residual_return, nan_median), y = cumulative_6m_residual_return)) +
  geom_hline(yintercept = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = scales::percent, limits = c(-0.15, 0.15)) +
  labs(
    title = "Resdiual Returns by Proxy Outcome",
    subtitle = "average monthly 6-month pre to 6-month post market adjusted return of target companies by value demand.",
    x = "Campaign Objective",
    y = "Cumulative Residual Return"
  )
```

```{r}
df %>%
  ggplot() +
  geom_boxplot(aes(x = reorder(campaign_objective_primary, cumulative_6m_residual_return, nan_median), y = cumulative_6m_residual_return)) +
  geom_hline(yintercept = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylim(-0.15, 0.15) +
  scale_y_continuous(labels = scales::percent, limits = c(-0.15, 0.15)) +
  labs(
    title = "Resdiual Returns by Campaign Objective",
    subtitle = "average monthly 6-month pre to 6-month post market adjusted return of target companies by value demand.",
    x = "Campaign Objective",
    y = "Cumulative Residual Return"
  )
```

```{r}
df %>%
  .[
    j = list(cumulative_6m_residual_return = mean(cumulative_6m_residual_return, na.rm = TRUE)),
    keyby = list(campaign_objective_primary)
  ] %>%
  ggplot() +
  geom_col(aes(
    x = reorder(campaign_objective_primary, cumulative_6m_residual_return, nan_median),
    y = cumulative_6m_residual_return)
  ) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "Cumulative Resdiual Returns by Campaign Objective",
    subtitle = "Cumulative 6-month pre to 6-month post market adjusted return of target companies by campaign objective.",
    x = "Campaign Objective",
    y = "Cumulative Residual Return"
  )
```

```{r}
df %>%
  .[
    j = list(cumulative_6m_residual_return = mean(cumulative_6m_residual_return, na.rm = TRUE)),
    keyby = list(campaign_objective_primary, proxy_campaign_result_group)
  ] %>%
  ggplot() +
  geom_col(aes(
    x = reorder(campaign_objective_primary, cumulative_6m_residual_return, nan_median),
    y = cumulative_6m_residual_return)
  ) +
  geom_hline(yintercept = 0) +
  facet_wrap(~proxy_campaign_result_group) +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "Cumulative Resdiual Returns by Campaign Objective",
    subtitle = "Cumulative 6-month pre to 6-month post market adjusted return of target companies by campaign objective.",
    x = "Campaign Objective",
    y = "Cumulative Residual Return"
  )
```

```{r}
df %>%
  ggplot() +
  geom_boxplot(aes(x = reorder(value_demand, cumulative_6m_residual_return, nan_median), y = cumulative_6m_residual_return)) +
  geom_hline(yintercept = 0) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(-0.15, 0.15) +
  labs(
    title = "Cumulative Resdiual Returns by Value Demand",
    subtitle = "Cumulative 6-month pre to 6-month post market adjusted return of target companies by value demand.",
    x = "Value Demand",
    y = "Cumulative Residual Return"
  )
```

```{r}
df %>%
  ggplot() +
  geom_boxplot(aes(x = reorder(governance_demand, cumulative_6m_residual_return, nan_median), y = cumulative_6m_residual_return)) +
  geom_hline(yintercept = 0) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(-0.15, 0.15) +
  labs(
    title = "Cumulative Resdiual Returns by Governance Demand",
    subtitle = "Cumulative 6-month pre to 6-month post market adjusted return of target companies by governance demand.",
    x = "Value Demand",
    y = "Cumulative Residual Return"
  )
```

## Return Sankeys

```{r}
df[, .N, by = list(value_demand_group, board_seats_result, return_result)] %>%
  .[board_seats_result %in% c("Management", "Dissident")] %>%
  ggplot(aes(axis1 = value_demand_group, axis2 = board_seats_result, axis3 = return_result, y = N)) +
  geom_alluvium(aes(fill = return_result)) +
  geom_stratum() +
  geom_text(stat = "stratum", label.strata = TRUE) +
  scale_x_discrete(limits = c("Value Demand", "Board Seats Result", "Return Result"), expand = c(.1, .05)) +
  theme_minimal() +
  labs(
    title = "Value Demands, Proxy Campaign Results and Return Result",
    subtitle = "Proportion of campaigns by value demand that lead to various proxy campaign and return outcomes."
  ) +
  theme(legend.position = 'bottom')
```


```{r}
df[, .N, by = list(value_demand_group, proxy_campaign_result_group, return_result)] %>%
  .[proxy_campaign_result_group %in% c("Management", "Dissident")] %>%
  ggplot(aes(axis1 = value_demand_group, axis2 = proxy_campaign_result_group, axis3 = return_result, y = N)) +
  geom_alluvium(aes(fill = return_result)) +
  geom_stratum() +
  geom_text(stat = "stratum", label.strata = TRUE) +
  scale_x_discrete(limits = c("Value Demand", "Proxy Campaign Result", "Return Result"), expand = c(.1, .05)) +
  theme_minimal() +
  labs(
    title = "Value Demands, Proxy Campaign Results and Return Result",
    subtitle = "Proportion of campaigns by value demand that lead to various proxy campaign and return outcomes."
  ) +
  theme(legend.position = 'bottom')
```

```{r}
df[, .N, by = list(campaign_objective_group, proxy_campaign_result_group, return_result)] %>%
  .[proxy_campaign_result_group %in% c("Management", "Dissident")] %>%
  ggplot(aes(axis1 = campaign_objective_group, axis2 = proxy_campaign_result_group, axis3 = return_result, y = N)) +
  geom_alluvium(aes(fill = return_result)) +
  geom_stratum() +
  geom_text(stat = "stratum", label.strata = TRUE) +
  scale_x_discrete(limits = c("Campaign Objective", "Proxy Campaign Result", "Return Result"), expand = c(.1, .05)) +
  theme_minimal() +
  labs(
    title = "Value Demands, Proxy Campaign Results and Return Result",
    subtitle = "Proportion of campaigns by value demand that lead to various proxy campaign and return outcomes."
  ) +
  theme(legend.position = 'bottom')
```

# Models

```{r}
df_model_data <- df %>%
  .[j = list(
    campaign_objective_primary,
    campaign_objective_group,
    value_demand,
    value_demand_group,
    governance_demand,
    earnings_yield_at_announcement,
    ownership_pecent_on_announcement,
    glass_lewis_support,
    iss_support,
    proxy_campaign_winner_or_result,
    proxy_campaign_result_group,
    board_seats_result
  )] 

df_proxy_data <- df_model_data %>%
  .[proxy_campaign_result_group %in% c("Dissident", "Management")] %>%
  .[, proxy_campaign_result_group := proxy_campaign_result_group %>% as.character %>% as_factor] 

df_board_data <- df_model_data %>%
  .[board_seats_result %in% c("Dissident", "Management")] %>%
  .[, board_seats_result := board_seats_result %>% as.character %>% as_factor] 
  
```

```{r}
glimpse(df_model_data)
```



    .[, positive_1_year_post_date_total_return := `1_year_post_date_total_return` >= 0] %>%
    .[, past_return := `1_year_pre_date_total_return`] %>%
    .[, earnings_yield := earnings_yield_at_announcement] %>%
    .[, objective := campaign_objective_group] %>%
    .[, result := proxy_result] %>%
    .[, positive_post_return := positive_1_year_post_date_total_return] %>%
    .[, post_return := `1_year_post_date_total_return`] %>%
    .[, positive_post_residual_return := `1_year_post_date_residual_return` >= 0] %>%
    .[, post_residual_return := `1_year_post_date_residual_return`] %>%
    .[, ownership := ownership_pecent_on_announcements]

```{r}
model <- glm(
  data = df_proxy_data,
  formula = (
    proxy_campaign_result_group ~
      value_demand_group +
      governance_demand + 
      campaign_objective_group +
      earnings_yield_at_announcement +
      ownership_pecent_on_announcement +
      glass_lewis_support +
      iss_support
  ),
  family = "binomial"
)

summary(model)

stargazer(model, type = "text")

df_model_coefficients <- model %>%
  broom::tidy() %>%
  as.data.table() %>%
  .[, odds_estimate := exp(estimate)] %>%
  .[, probability_estimate := odds_estimate / (1 + odds_estimate)]

print(df_model_coefficients %>% as.tibble())

df_model_coefficients %>%
  ggplot() +
  geom_col(aes(x = term, y = odds_estimate)) +
  geom_hline(yintercept = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "Odds Coefficients from Logistic Regression"
  )
```


```{r}
model <- glm(
  data = df_proxy_data,
  formula = (
    proxy_campaign_result_group ~
      value_demand_group +
      governance_demand + 
      campaign_objective_group +
      earnings_yield_at_announcement +
      ownership_pecent_on_announcement +
      glass_lewis_support +
      iss_support
  ),
  family = "binomial"
)

summary(model)

stargazer(model, type = "text")

df_model_coefficients <- model %>%
  broom::tidy() %>%
  as.data.table() %>%
  .[, odds_estimate := exp(estimate)] %>%
  .[, probability_estimate := odds_estimate / (1 + odds_estimate)]

print(df_model_coefficients %>% as.tibble())

df_model_coefficients %>%
  ggplot() +
  geom_col(aes(x = term, y = odds_estimate)) +
  geom_hline(yintercept = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    title = "Odds Coefficients from Logistic Regression"
  )
```
